Home

### 2025-11-18 index.qmd
changed paper link to google scholar and updated welcome

@@

[View all papers →](papers.qmd)

>>>>

## Welcome

Professor Bin Yu leads the Yu Group at UC Berkeley, an interdisciplinary team in
Statistics and EECS dedicated to advancing machine learning, artificial
intelligence, and veridical data science. Her group develops efficient and
interpretable ML/AI methods and theory—ranging from iterative random forests
(iRF) and FIGS to LoRA+ for model adaptation and CD-T and SPEX for interpreting
deep models. The Yu Group collaborates closely with domain experts in
neuroscience, genomics, and precision medicine.

A member of both the National Academy of Sciences and the American Academy of
Arts and Sciences, she has delivered major invited lectures, including the 2019
Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
(formerly Fisher Lecture). Her group’s PCS framework (predictability,
computability, and stability) for veridical data science has become an
influential guide for transparent, trustworthy data science and AI.

@@

[View all papers →](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en)
